---
title: "coffee-roulette"
author: "Genevieve Phillips"
date: "19/06/2020"
output: html_document
knit: (function(input, ...) {
    rmarkdown::render(
      input, output_dir = "./outputs/", 
      output_format = "html_document"
    )
  })
---

This code will run a 'coffee' roulette of sorts - it will pair people together with someone from another team (CSIRO / AAD / IMAS).

The code can be run multiple times, however I haven't included any functionality to stop the same pairing happening again and again through time. There would need to be some comparison of the output and then the code re-run - if anyone would like to add to / modify the code to do this, please, feel free to let me know how to do that!


```{r setup, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE, include = FALSE, warning = FALSE, message = FALSE)
knitr::opts_knit$set(root.dir = "./")
```

```{r load_data}
library(readr)
library(dplyr)
coffee <- read_csv("../data/coffee-roulette.csv") # this needs to have at a minimum, Name and Team. Need to modify code to add contact info.
df <- coffee %>% select(Name, Team)
```

```{r coffee_function}
coffee.function <- function(df,peeps){
  repeat{
test <- sample_n(df, peeps) #first coffee peep
test2 <- sample_n(df, peeps) #second coffee peep

if(test$Team != test2$Team) break #if these peeps are not in the same team, STOP!
  }
  test3 <- rbind(test, test2)
  }
```

```{r repeat_to_get_matches}
library(tidyr)
library(data.table)

coffee.time <- df[FALSE,]
coffee.time$pairing <- as.numeric() #this should be the repeats

for (i in 1:20){
  coffee.loop <- coffee.function(df, 1)
  coffee.loop$pairing <- i
  coffee.time <- unique(rbindlist(list(coffee.time, coffee.loop)), by = 'Name') #remove repeated Names
  
   }
  
coffee.schedule1 <- coffee.time %>%
  transform(pairing = as.factor(pairing)) %>%
  group_by(pairing) %>%
  mutate(n_people = n(), t = seq_along(pairing)) %>%
  filter(n_people == 2) %>% #remove matches with < 2 people
  mutate(buyer = if_else(t == 1, "buy coffee!", "choose venue!")) %>%
  select(Name, Team, pairing, buyer)


```


```{r round2}

df2 <- anti_join(df, coffee.schedule1, by = 'Name')
if (nrow(df2) >2){

coffee.time2 <- df2[FALSE,]
coffee.time2$pairing <- as.numeric() #this should be the repeats

for (i in 1:10){
  coffee.loop2 <- coffee.function(df2, 1)
  coffee.loop2$pairing <- i
  coffee.time2 <- unique(rbindlist(list(coffee.time2, coffee.loop2)), by = 'Name') #remove repeated Names
  
   }
  
coffee.schedule2 <- coffee.time2 %>%
  transform(pairing = as.factor(pairing)) %>%
  group_by(pairing) %>%
  mutate(n_people = n(), t = seq_along(pairing)) %>%
  filter(n_people == 2) %>% #remove matches with < 2 people
  mutate(buyer = if_else(t == 1, "buy coffee!", "choose venue!")) %>%
  select(Name, Team, pairing, buyer)

mid_schedule <- unique(rbindlist(list(coffee.schedule1, coffee.schedule2)), by = 'Name')
}else {mid_schedule <- coffee.schedule1}

```

```{r round3}

df3 <- anti_join(df, mid_schedule, by = 'Name')

if(nrow(df3) >2){

coffee.time3 <- df3[FALSE,]
coffee.time3$pairing <- as.numeric() #this should be the repeats

for (i in 1:10){
  coffee.loop3 <- coffee.function(df3, 1)
  coffee.loop3$pairing <- i
  coffee.time3 <- unique(rbindlist(list(coffee.time3, coffee.loop3)), by = 'Name') #remove repeated Names
  
   }
  
coffee.schedule3 <- coffee.time3 %>%
  transform(pairing = as.factor(pairing)) %>%
  group_by(pairing) %>%
  mutate(n_people = n(), t = seq_along(pairing)) %>%
  filter(n_people == 2) %>% #remove matches with < 2 people
  mutate(buyer = if_else(t == 1, "buy coffee!", "choose venue!")) %>%
  select(Name, Team, pairing, buyer)

final_schedule <- unique(rbindlist(list(mid_schedule, coffee.schedule3)), by = 'Name')
} else{final_schedule <- mid_schedule}

```

```{r missing}
missing <- anti_join(df, final_schedule)

if(nrow(missing) > 2){
  coffee.time4 <- missing[FALSE,]
coffee.time4$pairing <- as.numeric() #this should be the repeats

for (i in 1:10){
  coffee.loop4 <- coffee.function(missing, 1)
  coffee.loop4$pairing <- i
  coffee.time4 <- unique(rbindlist(list(coffee.time4, coffee.loop4)), by = 'Name') #remove repeated Names
  
   }
  
coffee.schedule4 <- coffee.time4 %>%
  transform(pairing = as.factor(pairing)) %>%
  group_by(pairing) %>%
  mutate(n_people = n(), t = seq_along(pairing)) %>%
  filter(n_people == 2) %>% #remove matches with < 2 people
  mutate(buyer = if_else(t == 1, "buy coffee!", "choose venue!")) %>%
  select(Name, Team, pairing, buyer)

final_final_schedule <- unique(rbindlist(list(final_schedule, coffee.schedule4)), by = 'Name')
} else{final_final_schedule <- final_schedule}


wtf <- anti_join(df, final_final_schedule, by='Name')


```

## Coffee Pairings

```{r coffee_schedule, include = TRUE}

library(knitr)

# kable(coffee.schedule)
kable(final_final_schedule)
```

## These people have a bye this week

```{r bye_schedule, include = TRUE}

kable(wtf)
```

